SMT-Boosted Security Types for Low-Level MPC

### 2025-11-08 toplas26/metalang.tex
checkpoint

\begin{lemma}
  \label{lemma-genentails}
  If $\forall y_1:\tau_1,\ldots,y_n:\tau_n . \peq_1 \models \peq_2$ and
  $\peq_1[\mv_1/y_1]\cdots[\mv_n/y_n] \redx \eqs_1$ and
  $\peq_2[\mv_1/y_1]\cdots[\mv_n/y_n] \redx \eqs_2$, then
  $\eqs_1 \models \eqs_2$.  
\end{lemma}

>>>>

\begin{lemma}
  \label{lemma-fresh}
  Given $\eqs$ and $w, \cid = \fresh(\mathit{string}, \mathit{cid})$ and
  some $w',\cid'$ where 
  $\peq[w/y_1,\cid/y_n] \redx \eqs$ and
  $\peq[w'/y_1,\cid'/y_n] \redx \eqs'$.
  Then $\store \models \eqs'$ implies $\store \models \eqs$. 
\end{lemma}

\begin{proof}
  If $w',\cid'$ are fresh or chosen the result is
  trivial.  Otherwise, it must be the case that at least two
  distinct variables $x_1$ and $x_2$ in $\eqs$ are renamed as a single
  variable $x$ in $\eqs'$, given freshness of $w,\cid$. Let
  $\mathit{rename}$ be the function that maps variables in $\eqs$ to
  variables in $\eqs'$ such that $\mathit{rename}(\eqs) = \eqs'$. Assume
  $\store' \models \eqs'$, and define $\store$ such that:
  $$
  \forall x \in \dom(\vars(E)) . \store(x) \defeq \store'(\mathit{rename}(x)) 
  $$
  Then $\store$ must be a model of $\eqs$, which is a contradiction. 
\end{proof}

\begin{lemma}
  \label{lemma-genentails}
  If $\forall y_1:\tau_1,\ldots,y_n:\tau_n . \peq_1 \models \peq_2$ and
  $\peq_1[\mv_1/y_1]\cdots[\mv_n/y_n] \redx \eqs_1$ and
  $\peq_2[\mv_1/y_1]\cdots[\mv_n/y_n] \redx \eqs_2$, then
  $\eqs_1 \models \eqs_2$.  
\end{lemma}
\begin{proof}
  By assumption and definition of \TirName{GenEntails} we have
  $\peq_1[\mv_1'/y_n \cdots \mv_n'/y_n] \redx \eqs_1'$ and
  $\peq_2[\mv_1'/y_n \cdots \mv_n'/y_n] \redx \eqs_2'$ and $\eqs_1'
  \models \eqs_2'$ for some $\mv_1',\ldots,\mv_n' =
  \fresh(\tau_1,\ldots,\tau_n)$.  Now suppose on the contrary that
  $\eqs_1 \not\models \eqs_2$.  This implies the existence of $\store$
  such that $\store \models \eqs_1$ and $\store \not\models \eqs_2$.
  But Lemma \ref{lemma-fresh} implies that $\store \models \eqs_1'$,
  so by definition we have $\store \models \eqs_2'$ implying $\store
  \models \eqs_2$ by construction, which is a contradiction.
\end{proof}
